MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd

### BP Again ??? XXX
```{r}
#now, start works
BP_dataset2 <- na.omit(NPP_forest[,c("tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset2)
a2 <- stepwise(BP_dataset2,"tnpp_a")
a2[[1]]
a2[[2]]
a2[[3]]
bp_model <- (lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+(1|site_a),data=BP_dataset2))
summary(bp_model)
r.squaredGLMM(bp_model)

@@

### ANPP again? XXX
```{r}
anpp_tnpp_dataset2 <- na.omit(NPP_forest[,c("anpp_tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(subset(NPP_forest,ANPP_2>0))
model2a <- stepwise(anpp_tnpp_dataset2,"anpp_tnpp_a")
model2a[[1]]
model2a[[2]]
model2a[[3]]
anpp_tnpp_model <- (lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(anpp_tnpp_model)
r.squaredGLMM(anpp_tnpp_model)

@@

XXX this is about NRE, but section 'NRE' above as well 
```{r}
#NRE = 69%
NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

@@

### ???
XXX what is this figure?
```{r}
gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_CNrt")]),varnam = "nue_CNrt",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15);g2 <- gg$gglegend

@@

### ???
XXX what is this figure?
```{r warning=FALSE}
#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","CNrt")]),varnam = "CNrt",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

## Plot???

XXX What plot?
```{r}

@@

## Fit models

@@

## Plot partial dependencies
```{r}

@@

## XXX ???
```{r}

#nuptake figure
#N minerlization
Nmin_statistical <- subset(NPP_forest,Nmin>0)

@@

## XXX ??
```{r}

@@

## XXX ?
```{r}
# n uptake
mod_nue3 <- (lm(pred_nuptake~LMA_a+fAPAR_a+age_a+vpd_a+CNrt_a+Tg_a+vcmax25_a+PPFD_a,data=nue_allplots))
summary(mod_nue3)
nue1c <- visreg(mod_nue3,"LMA_a",type="contrast")
nue2c <- visreg(mod_nue3,"fAPAR_a",type="contrast")
nue3c <- visreg(mod_nue3,"age_a",type="contrast")
nue4c <- visreg(mod_nue3,"vpd_a",type="contrast")
nue5c <- visreg(mod_nue3,"CNrt_a",type="contrast")
nue6c <- visreg(mod_nue3,"Tg_a",type="contrast")
nue7c <- visreg(mod_nue3,"vcmax25_a",type="contrast")
nue8c <- visreg(mod_nue3,"PPFD_a",type="contrast")

@@

## XXX ???
```{r}
#validation - N uptake
Nmin_statistical$pred_nuptake

@@

## XXX what figure does this produce? 
```{r}
#visreg

@@

### XXX?
```{r}
#all statistics
#forest
sum(uncertainty_npp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_anpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_nuptake*(forest_percent *conversion)*available_grid2,na.rm=TRUE)

@@

### XXX?
```{r}
#partial residual figure
BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
bp_model <- (lmer(tnpp_a~Tg_a+PPFD_a+soilCN_a+obs_age_a+observedfAPAR_a+(1|site_a),data=BP_dataset))
summary(bp_model)

>>>>

### BP vs. model predictors

```{r}
#now, start works
BP_dataset2 <- na.omit(NPP_forest[,c("tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(BP_dataset2)
a2 <- stepwise(BP_dataset2,"tnpp_a")
a2[[1]]
a2[[2]]
a2[[3]]
bp_model <- (lmer(tnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+(1|site_a),data=BP_dataset2))
summary(bp_model)
r.squaredGLMM(bp_model)

@@

### ANPP vs. modelled predictors

```{r}
anpp_tnpp_dataset2 <- na.omit(NPP_forest[,c("anpp_tnpp_a","age_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
dim(subset(NPP_forest,ANPP_2>0))
model2a <- stepwise(anpp_tnpp_dataset2,"anpp_tnpp_a")
model2a[[1]]
model2a[[2]]
model2a[[3]]
anpp_tnpp_model <- (lmer(anpp_tnpp_a~CNrt_a+PPFD_a+Tg_a+age_a+(1|site_a),data=anpp_tnpp_dataset2))
summary(anpp_tnpp_model)
r.squaredGLMM(anpp_tnpp_model)

@@

```{r}
#NRE = 69%
NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

@@

### Global maps for effect of each factor NUE (not used now)

```{r}
gg <- plot_map3(na.omit(nue_all[,c("lon","lat","nue_CNrt")]),varnam = "nue_CNrt",latmin = -65, latmax = 85,combine=FALSE,
                colorscale = c( "royalblue4", "wheat","tomato3"),
                breaks = seq(-0.05,0.05,0.01))
g1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15);g2 <- gg$gglegend

@@

### Global maps of each predictors

```{r warning=FALSE}
#figs2 representing all predictors
gg <- plot_map3(na.omit(CNrt[,c("lon","lat","CNrt")]),varnam = "CNrt",latmin = -65, latmax = 85,combine=FALSE)
d1 <- gg$ggmap +labs(title = "Soil C/N")+theme_grey(base_size = 15)+ white;d2 <- gg$gglegend+ white

@@

## BP

```{r}

@@

### Fit models

@@

### Plot partial dependencies
```{r}

@@

## N uptake

```{r}
#nuptake figure
#N minerlization
Nmin_statistical <- subset(NPP_forest,Nmin>0)

@@

### NUE

```{r}

@@

## Nuptake or NUE vs. all predictors

```{r}
# n uptake
mod_nue3 <- (lm(pred_nuptake~LMA_a+fAPAR_a+age_a+vpd_a+CNrt_a+Tg_a+vcmax25_a+PPFD_a,data=nue_allplots))
summary(mod_nue3)
nue1c <- visreg(mod_nue3,"LMA_a",type="contrast")
nue2c <- visreg(mod_nue3,"fAPAR_a",type="contrast")
nue3c <- visreg(mod_nue3,"age_a",type="contrast")
nue4c <- visreg(mod_nue3,"vpd_a",type="contrast")
nue5c <- visreg(mod_nue3,"CNrt_a",type="contrast")
nue6c <- visreg(mod_nue3,"Tg_a",type="contrast")
nue7c <- visreg(mod_nue3,"vcmax25_a",type="contrast")
nue8c <- visreg(mod_nue3,"PPFD_a",type="contrast")

@@

## N uptake validation between models

```{r}
#validation - N uptake
Nmin_statistical$pred_nuptake

@@

### visreg for BP and anpp/bp vs. all measured predictors
```{r}
#visreg

@@

### statistics of uncertainty

```{r}
#all statistics
#forest
sum(uncertainty_npp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_anpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnpp*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_lnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_wnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_bnf*(forest_percent *conversion)*available_grid2,na.rm=TRUE)
sum(uncertainty_nuptake*(forest_percent *conversion)*available_grid2,na.rm=TRUE)

@@

### BP partial relationship vs. observations

```{r}
#partial residual figure
BP_dataset <- na.omit(NPP_forest[,c("tnpp_a","obs_age_a","observedfAPAR_a","soilCN_a","Tg_a","PPFD_a","vpd_a","site_a")])
#model1 <- stepwise(BP_dataset,"tnpp_a")
#model1[[1]]
#model1[[2]]
bp_model <- (lmer(tnpp_a~Tg_a+PPFD_a+soilCN_a+obs_age_a+observedfAPAR_a+(1|site_a),data=BP_dataset))
summary(bp_model)
